### 2018-05-17 Paper/examples.tex
..

>>>>

In order to verify the accuracy of the third-order PCE, we estimate the relative L-2 norm of the
difference between predictions of  $g(\bm{X})$, obtained using the actual function in ~\eqref{eq:limit}
and the PCE using~\eqref{eq:l2}.  The value of $\epsilon_{\mbox{\tiny{L-2}}}$ using evaluations at
100 points was found to be 0.0835 i.e. the third-order PCE is accurate within 8.36$\%$. Furthermore, 
the accuracy is assessed in a probabilistic sense by comparing PDFs
of $g(\bm{X})$, obtained using the function and the 3D PCE as illustrated in Figure~\ref{fig:conv_osc}~(right).
Clearly, the two PDFs are in excellent agreement with each other. Hence, the ROS constructed 
using the methodology presented in section~\ref{sec:method} could be used reliably to characterize
as well as quantify the uncertainty in $g(\bm{X})$ due to parametric uncertainty associated with
its functional description in~\eqref{eq:limit}, efficiently.
